Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-08 paper/main.tex
cleaning todos2

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% What we do
In the current study, we exploratorily tested if spatial information embedded in
a Hollywood movie and its audio-description of (i.e. the movie's soundtrack with
an additional narrator) correlates with increased hemodynamic activity in the
PPA.
%
We use publicly available functional magnetic resonance imaging data
(studyforrest.org) of 14 subjects to build canonical general linear model (GLM)
$t$-contrasts and compare current results to results that we gained from a
dedicated visual localizer experiment conducted with same participants.
% compare to visual localizer experiment group results
On a group average level, results of our whole brain analyses show significantly
increased activation restricted to the anterior part of the PPA that was defined
using the visual localizer [as well as in the retrosplenial and lateral
occipital cortex] of both hemispheres.
% individual results
On an individual level, results show significant bilateral clusters in the
anterior PPA of nine subjects and significant unilateral clusters in two
subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of auditorily presented spatial
information.
% conclusion: PPA has subregions
Lastly, our results provides further evidence that the PPA can be divided into
functional subregions.\todo{kinda bold statements; this depends on the data \&
discussion}\end{abstract}

@@

% AO annotation
For the analysis of the AO stumulus, we extended a publicly available annotation
of speech \citep{haeusler2020speechanno} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content based on a set of rules.
% reference to table with rules and examples
A complete overview of all 18 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in
a] disco'', ``[the platoon wades through a] rice field''). They also comprise
words that could count as a member of another categories in case the narrator
uses these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').

@@

% AO: primary contrast
In the primary contrast of the AO stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all non-geometry related categories (\texttt{body},
\texttt{bodypart}, \texttt{fahead}, \texttt{object}, \texttt{sex\_f},
\texttt{sex\_m}) except \texttt{furniture}.

% why se_new & se_old were not used in the primary contrasts
The categories of nouns cueing a setting that occured for the first time
(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived differently by
different subjects as either a geometry-defining scene element or as an isolated
object.

% AV primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed these categories on average best represent events that trigger
perception of space versus objects or faces.\todo{syntax?}

@@

\todo[inline]{SE: sauber differenzieren zwischen "Lokalisation der PPA" und
    "Antwortverhalten einer vorab definierten PPA". Ich habe den Eindruck, dass
Du oft das erste machst es aber als das zweite beschreibst}

\todo[inline]{SE: Vergleich mit VIS kommt bestenfalls en passant; VIS selber
wird gar nicht berichtet, wäre aber wichtig zum Andocken an Literatur}

\todo[inline]{SE: würde wetten, dass Reviewer fragen: Wie sieht es im vergleich
dazu mit Faces aus?}

@@

\todo[inline]{SE: Wie sehen die Antworten innerhalb der "klassisch definierten" PPA für die verschiedenen regressoren bzw. kategorien derselben (zumindest aber places vs faces) aus?}

\todo[inline]{individual results: AO trifft besser die VIS-PPA "trifft" als AV. Das ist zumindest sehr überraschend, oder?}

\todo[inline]{Bland-Altman-Plots: Welche Areale habt ihr als masks
genommen, FFA ist ja kartiert (Julia Caspers)}

@@

\todo[inline]{SE: RSC etc: Irgendwie waren die bis zu Diskussion eher ein
afterthought. Daher etwas überraschend, vielleicht in Einleitung und Results
schon mehr bringen}

>>>>

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% What we do
In the current study, we exploratorily tested if spatial information embedded in
a Hollywood movie and its audio-description of (i.e. the movie's soundtrack with
an additional narrator) correlates with increased hemodynamic activity in the
PPA.
%
We use publicly available functional magnetic resonance imaging data
(studyforrest.org) of 14 subjects to build canonical general linear model (GLM)
$t$-contrasts and compare current results to results that we gained from a
dedicated visual localizer experiment conducted with same participants.
% compare to visual localizer experiment group results
On a group average level, results of our whole brain analyses show significantly
increased activation restricted to the anterior part of the PPA that was defined
using the visual localizer [as well as in the retrosplenial and lateral
occipital cortex] of both hemispheres.
% individual results
On an individual level, results show significant bilateral clusters in the
anterior PPA of nine subjects and significant unilateral clusters in two
subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of auditorily presented spatial
information.
% conclusion: PPA has subregions
Lastly, our results provides further evidence that the PPA can be divided into
functional subregions.\end{abstract}

@@

% AO annotation
For the analysis of the AO stumulus, we extended a publicly available annotation
of speech \citep{haeusler2020speechanno} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content based on a set of rules.
% reference to table with rules and examples
A complete overview of all 18 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in
a] disco'', ``[the platoon wades through a] rice field''). They also comprise
words that could count as a member of another categories in case the narrator
uses these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').

@@

% AO: primary contrast
In the primary contrast of the AO stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all non-geometry related categories (\texttt{body},
\texttt{bodypart}, \texttt{fahead}, \texttt{object}, \texttt{sex\_f},
\texttt{sex\_m}) except \texttt{furniture}.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns cueing a setting that occured for the first time
(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived differently by
different subjects as either a geometry-defining scene element or as an isolated
object.

% AV primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that movie frames in these categories on average best represent
events that trigger perception of space versus objects or faces.\todo{syntax?}

@@

\todo[inline]{SE: sauber differenzieren zwischen "Lokalisation der PPA" und
    "Antwortverhalten einer vorab definierten PPA". Ich habe den Eindruck, dass
Du oft das erste machst es aber als das zweite beschreibst; COH: ??? we do
whole-brain analysies, so probably ``localization'', }

\todo[inline]{SE: Vergleich mit VIS kommt bestenfalls en passant; VIS selber
wird gar nicht berichtet, wäre aber wichtig zum Andocken an Literatur; COH: }

\todo[inline]{SE: würde wetten, dass Reviewer fragen: Wie sieht es im vergleich
dazu mit Faces aus? COH: yeah, well, I made the contrasts similar to Sengupta
and considered the contrast to an average of all ``non-spatial'' stuff
appropriate; should be cleare in the method section (s. ``Contrasts'')}

@@

\todo[inline]{SE: Wie sehen die Antworten innerhalb der "klassisch definierten"
PPA für die verschiedenen regressoren bzw. kategorien derselben (zumindest aber
places vs faces) aus? COH: ???}

\todo[inline]{individual results: AO trifft besser die VIS-PPA "trifft" als AV.
Das ist zumindest sehr überraschend, oder?; COH: actually it isn't because the
of blindly averaging the actual frame content in the categories of movie cuts
(cf. shortcomings); this ``cross-modal control things'' seems to more confuse
than having its merits}

\todo[inline]{Bland-Altman-Plots: Welche Areale habt ihr als masks
genommen, FFA ist ja kartiert (Julia Caspers); COH: probaly the caption was
invisible in the version Simon got? changed the size of the figure so the
caption is now on the page}

@@

\todo[inline]{SE: RSC etc: Irgendwie waren die bis zu Diskussion eher ein
afterthought. Daher etwas überraschend, vielleicht in Einleitung und Results
schon mehr bringen; COH: afterthought, for sure; It was highly probable that RSC
would show up but it wasn't aim of the study (had no ROIs for it anyway); imo
this is an issue of story telling vs. hypotheses after results}
